### 2008-08-12 doc/glite_gateway/glite_gateway.tex
Major modification on the document

\def\documenttitle{The ARC gLite Gateway}
\captionsetup{margin=20pt,font={footnotesize, it},labelfont=bf}
\begin{document}
\def\today{\number\day/\number\month/\number\year}
\begin{titlepage}

@@

{\raggedleft Knowarc\_D3.2-1\_08\par}

@@

@@

The purpose of this document is to describe how Advanced Resource Connector version 1 (ARC1\footnote{\url{http://www.nordugrid.org/}}) users can execute grid jobs on EGEE CREAM2\footnote{\url{http://grid.pd.infn.it/cream/}} resources.\par In sections \ref{Introduction} and \ref{Interoperability} a brief introduction on interoperability issues will be given. Section \ref{Building} describes how to build the gateway library, section \ref{Users guide} shows how it can be used. Section \ref{Developers notes} gives a tiny developer-oriented introduction on how the gateway library is built up, while section \ref{Outstanding issues} addresses the current issues with the code. Section \ref{Conclusions} concludes the technical document.
\section{Interoperability}
\label{Interoperability}

@@

\item or to use standard or close-to-standard interfaces on both sides.

@@

The latter solution which is preferred from standardization point of view and also has been chosen by ARC1 developers is illustrated in figure \ref{fig:Chart 1}.\par

@@

\caption{\label{fig:Chart 1}This chart illustrates how the ARC1$\rightarrow$gLite gateway library works in general. After successful authentication and credential delegation to the CREAM2 resource, users submit grid jobs through it.  A wrapper script at the computing element may pull input files from different storage elements using storage protocol, say, GridFTP. Users get job information through CREAM2 and may send management commands, like kill a job or undelegate credentials.} }

@@

\section{CREAM2}
The main purpose of this project was to provide access to gLite CREAM2-enabled resources from ARC1 user interface, but not the other way around: i.e. accessing ARC resources from gLite is addressed in the EGEE project\footnote{\url{http://www.eu-egee.org/}}.\par

@@

\item It is a web service interface that fits to the built-in web service implementation of ARC1.
\item It contains numerous improvements compared to the original CREAM interface. (Unfortunately CREAM2 is not backwards compatible with CREAM.)
\item It supports job status queries compared to the other web service interfaces of gLite, like WMProxy.
\item It is an official interface to gLite computing elements and as EGEE evolves it is expected that more and more computing elements will have CREAM2 interfaces.

@@

\section{Building, dependencies}
\subsection{Generic installation disciplines}
\label{Building}
The ARC$\rightarrow$gLite gateway software is incorporated into ARC1 releases, so you only need to download either the freshest ARC1 from the source tree\footnote{\url{http://svn.nordugrid.org/}} and compile it or to install it from package\footnote{\url{http://download.nordugrid.org/software/nordugrid-arc1/}}.\par
The gateway library code has two dependencies:
\item Globus Toolkit is needed to enable GridFTP functionality to be able to upload input files from the user interface to the CREAM computing node.
\item VOMS is needed to allow users authentication on a CREAM resource.
In both cases it is highly recommended to download these pieces of software along with their NorduGrid-specific Globus\footnote{\url{http://download.nordugrid.org/software/globus/}} and VOMS\footnote{\url{http://download.nordugrid.org/software/voms/}} patches from the NorduGrid repository. In case you are interested in the details of patching, then consult the NorduGrid wiki page\footnote{\url{http://wiki.nordugrid.org/images/4/46/NorduGrid-globus.patch.txt}}. It might also be interesting to read how to compile Globus Toolkit. Some more details on this topic can be found on the NorduGrid Globus compilation page\footnote{\url{http://wiki.nordugrid.org/index.php/Globus\_Libraries}}. There are also some details on how to compile VOMS from source at NorduGrid VOMS compilation page\footnote{\url{http://wiki.nordugrid.org/index.php/VOMS\_compiling\_detailes}}.
\subsection{Software installation on Debian Linux}
This section contains instructions how to install the software onto Debian Linux.
\item Put the Debian repository into the APT source files (/etc/apt/sources.list).
\item Update the package list and install the necessary dependencies.
\item Configure the Globus libraries.
\item Install ARC1 client. There is a broken dependency that installs separately.
\item Install Globus and VOMS specific files.
\begin{shaded}\verb#$ mkdir -p /opt/glite/etc/#\\*\end{shaded}
and copy these lines into the vomses file located /opt/glite/etc/vomses
\section{Using the ARC${\rightarrow}$gLite Gateway from the Command Line}

@@

@@

Before getting into the details of the gatewy toolkit, the authentication and authorization processes need clarification.\par
In the different grid systems the most widespread authentication method is the certificate based authentication. GLite also requires VOMS-enabled proxy X509 certificates to access resources. It means that you should be a member of the Virtual Organisation that is valid on the remote site. If the VOMS package has been correctly installed then the following command provides the necessary VOMS proxy certificate.\par
\begin{shaded}\verb#$ voms-proxy-init -voms <Your Virtual Organisation>#\end{shaded}

@@

CREAM2 service URLs can directly be downloaded from any BDII database of gLite using the following LDAP command:
\verb#$ ldapsearch -x -h lcg-bdii.cern.ch -p 2170 -b o=grid '(GlueCEUniqueID=*blah*)'#
or
\verb#$ ldapsearch -x -h lxbra2305.cern.ch -p 2170 -b mds-vo-name=local,o=grid \#\\*
\verb#        '(GlueCEUniqueID=*cream*)' | grep GlueCEInfoContactString | \#\\*
\verb#        awk '{print $2}' | sort | uniq#

\subsection{glitedelegate}
\label{glitedelegate}
If you want to submit a job to a gLite server, first you have to own a valid delegation on the remote site. You can either use an old, but still valid delegation identifier, or register a new one. There is a command line tool to register a delegation on the resource to be used.\par
The usage is very easy and straighforward. All you need is a working CREAM2 service URL, and a locally unique arbitrary delegation ID. This delegation ID will be associated to the remote resource. If you are not sure wether your favourite delegation ID is occupied or not, then try to delete it before registering it again. (See Section \ref{gliteundelegate} for further details!) The delegation command has the following syntax:
\begin{shaded}\verb#$ glitedelegate <delegation ID> <service URL>#\end{shaded}
For example:
\begin{shaded}\verb#$ glitedelegate test_delegation \#\\*
\verb#        https://cream.grid.upjs.sk:8443/ce-cream/services/gridsite-delegation#\end{shaded}
\subsection{glitesub}
\label{glitesub}
In the previous section it was shown how to create delegation. (See Section \ref{glitedelegate}!) This function, the job submission, is the only one which needs the delegation ID.\par The next step is to prepare the necessary input files and the job description!\par
The glitesub command syntax is the following:
\begin{shaded}\verb#$ glitesub -D <delegation ID> <service URL> <job description> <info file>#\end{shaded}
Here the delegation ID is the previously registered identification. The service URL will be different than in the delegation example above, because this is not the URL of the delegation, but the execution service. The job description must be in JDL format like in the example below. The info file stores information about job submitted. It should either be a non-existing file or it is overwritten. This file contains the job ID, the input sandbox URL, the output sandbox URL and the service URL. The submission command will take care of uploading the necessary input files up to the execution node.\par
It is important that the \textit{VirtualOrganisation} and \textit{QueueName} attributes should be the same as your virtual organisation name and the corresponding queue name on the server side.\par

An example JDL description:\\
\begin{minipage}{\textwidth}
\verb#[#\\
\verb#Executable = "/bin/hostname";#\\
\verb#StdInput = "std.in";#\\
\verb#StdOutput = "std.out";#\\
\verb#StdError = "std.err";#\\
\verb#BatchSystem = "pbs";#\\
\verb#VirtualOrganisation = "knowarc.eu";#\\
\verb#InputSandbox = {"std.in"};#\\
\verb#OutputSandbox = {"std.out","std.err"};#\\
\verb#QueueName = "knowarc.eu";#\\
\verb#OutputSandboxDestURI = { "gsiftp://localhost/std.out", "gsiftp://localhost/std.err" };#\\
\verb#]#
\end{minipage}

@@

@@

The \textbf{glitestat} tool extracts job information about a CREAM2 job identified by the information file. This file made by command \textbf{glitesub} is the only argument needed here.\par

@@

The possible responses and their meanings are the following:

@@

\item ACCEPTING - The job submission is comleted but the job is not yet scheduled
\item SUBMITTING - Scheduling in progress
\item INLRMS:Q - The job is already at the local resource manager system and it is queued
\item INLRMS:R - The job is waiting at the local resource manager system for running
\item INLRMS:S - The job is actually running
\item KILLED - The job was terminated
\item FINISHED - The job has finished
\item FAILED - The job had some failure
\item FAILES - The job had some failure at LRMS level
\item EXECUTED - The job has been finished and there is no stating information available

@@

The \textbf{glitekill} command can be used for killing a remote job. The only necessary argument is the information file made by \textbf{glitesub}. (See Section \ref{glitesub} for further details!) This command initiates stopping the job. You can check the effect by using \textbf{glitestat}. (See Section \ref{glitestat} for its usage!)\par

@@

Either after killing a job or because of some remote error occurs garbage files may remain on the server. These files can be purged by using command \textbf{gliteclean}. If you intentionally kill a job on the computing node, the job related stuff might also remain as garbage in the remote queue. This command also removes the job from the gLite server queue. It is important to note that this command removes the local information file as well. It is very useful to run this command after killing a job. (See Section \ref{glitekill}!)\par

@@

After your work is complete it is possible to unregister and delete the delegation entry from the remote site by using command \textbf{gliteundelegate}. You can also use it, if you want to register a delegation ID but are unsure whether it is used or not. Put the delegation service URL into the argument!\par

@@

\begin{shaded}\verb#$ gliteundelegate <delegation ID> <service URL>#\end{shaded}

@@

\section{Developers notes}
\label{Developers notes}
This section describes how to use the library on your own client. The base class of the gLite client is written as an ARC Client Component (ACC) but also can be used as a standalone library. There is nothing more to be done just to link the \textbf{CREAMClient}, \textbf{arcclient} and \textbf{arccommon} libraries installed with the ARC1 sofware and to create an instance of the \textit{CREAMClient} class.\par
This client object has a very easy-to-use and intuitive interface. It uses the VOMS proxy certificate to build the secure channel to the server and to sign that of the server's. Actually the client looks for this certificate just at its default location. If you want to store it somewhere else, you have to modify the source code itself.\par
The following sections present the set of functions provided by the library.
\subsection{CREAMClient(Arc::URL, Arc::MCCConfig)}
\subsection{setDelegationId(std::string)}
\subsection{createDelegation(std::string)}
As almost every funtion, this one has no return value either. If there are any problems during the communication, either locally in the channel or at the remote site, the function throws \textit{CREAMClientError} described previously. If there are no exceptions thrown, then the command is considered to have been successfully completed.
\subsection{destroyDelegation(std::string)}
This method has the reverse functionality of the \textbf{createDelegation} function. It sends the CREAM2 \textit{destroy} message to the remote server.
\subsection{submit(std::string)}
\subsection{stat(std::string)}
\subsection{cancel(std::string)}
\subsection{purge(std::string)}
\subsection{An example gLite client}
Finally, here is an example code to present how easy and simple is to write a new client. This code sample requests the job status of a previously submitted remote job, and writes it to the standard output. The client is written in C++.

@@

\section{Outstanding issues}
\label{Outstanding issues}

@@

@@

>>>>

\def\documenttitle{NOT\_READY\_The glite gateway plugin of ARCLIB and related command line tools}
\captionsetup{margin=20pt,font={footnotesize, it},labelfont=bf}
\begin{document}
\def\today{\number\day/\number\month/\number\year}
\begin{titlepage}

@@

{\raggedleft NORDUGRID-TECH-22\par}

@@

{\centering \large Mattias Ellert\footnote{mattias.ellert@fysast.uu.se} \large \par}

@@

The purpose of this document is to describe this gLite specific plugin of the ARCLIB (Hivatkozni: jövőbeli Deliverable) to present the related command line utilities built on top of these libraries. The gateway library together with the tools enables seemless interoparability with gLite computing elements. It is possible, that relevant sections of this document will be moved into ARC1 userguide and into ARCLIB technical documentation. Interoperability with gLite storage element is provided by an other set of ARC library. This data library provides native interfaces to GridFTP SRM which is the main bulding blocks of a gLite storage element. A storage interopability is out of scope of this library.
\section{Overview}
\label{Overview}

@@

\item or to explicitly implement the interface of the other side in the client.

@@

The latter solution was preferred by ARC1 developers, the gLite gateway library module has been implemented in the ARCLIB and the gateway functionality will be transparently offered via the usual Nordugrid command line tools. An overview of the preferred soulution is presented in figure \ref{fig:Chart 1}.\par

@@

\caption{\label{fig:Chart 1}This chart illustrates how the ARC1$\rightarrow$gLite gateway library module based approach works. The user will be able to express his requirements in the job description document using any of the xRSL, JDL or JSDL languages. The ARC client library will perform an automatic transformation. The gLite gateway functionality integrated into the ARCLIB, thus into the ARC client enables the user to transparently access gLite computing resources via the usual ARC command line tools. The gLite modules perform authentication, credential delagation and job submission to the CREAM2 CE. The CREAM2 CE may perform the necessary input file download from the different storage element. The library module gets job information through CREAM2 and sends management commands, like kill a job or undelegate credentials. Note, that not all the functionality described on the overview figure is implemented yet, for the current limitations see section \ref{Current limitations}!}}

@@

\subsection{The supported gLite CE interface: CREAM2}
The gLite computing element (CE) offers several interfaces. Some of them are only suitabe for the WMS (glite resource broker) and was not meant to be used by 3rd party clients. Fortunately gLite comes with a webservice based computing element interface, known as the CREAM CE. The CREAM has undergone several major revisions. We can only hope that some stability will soon arise. The current CREAM version has entered the EGEE certification process newertheless it is a full scale deplomeyment on the EGEE worldwide grid has not taken place yet. CREAM2 is available on several preproduction and testing grid sites.\par
Nevertheless the KnowARC project chose the CREAM version 2\cite{cream} as the gLite computing element interface.\par ... Hivatkozás a cikkre, mint CREAM-re...
In particular, the gateway library was developed against version glite-ce-cream\_R\_1\_8\_3\_0\footnote{\url{http://grid.pd.infn.it/cream/field.php?n=Main.ReleaseNotes}}.\par

@@

\item CREAM2 has a web service interface that fits the web service based ARC1.
\item CREAM2 enables direct access to the gLite computing element without the need of going through the WMS.
\item CREAM2 contains numerous improvements compared to the earlier CREAM versions.
\item Unlike the other gLite CE interfaces it supports direct job status queries 
\item It is an official interface to gLite computing elements and as EGEE evolves it is expected that more and more computing elements will be deployed with CREAM2 interface.
\item CREAM2 offers a convenient way of handling input and output files through accessing the input and output sandbox via GridFTP.

@@

In the near future CREAM will offer yet another interface which will be based on the BES/JSDL/GLUE OGF standards. This CREAM BES interface will coexists with the CREAM2 too.\par
\section{External dependencies and installation instructions}
\label{External dependencies and installation instructions}
The ARCLIB gLite plugin have only one dependency. GridFTP components of the Globus Toolkit are needed to enable data staging functionality to those CREAM2 computing elements which offer input and output sandbox over a GridFTP enabled storage. Unfortunately the gateway library only works together with a strongly patched Globus verion. The Nordugrid patched Globus can be dowloaded from the Nordugrid download area\footnote{\url{http://download.nordugrid.org/software/globus/}}. Further information about the Nordugrid Globus patches can be read on the Nordugrid page\footnote{\url{http://wiki.nordugrid.org/index.php/Globus\_Libraries}}. It is worth to mention that the user will need a VOMS proxy certificate in order to use the command line tools against a CREAM2 service. This VOMS proxy can be generated by using the VOMS client tools. It is only the VOMS enabled proxy certificate that is needed here, appart from this no VOMS component needed.\par
The ARC gLite gateway plugin library and the temporary command line utilities are incorporated into ARC1 releases. The source code is available from the ARC1 SVN repository\footnote{\url{http://svn.nordugrid.org/repos/nordugrid/arc1/}} and binary packages are provided at the Nordugrid download area. The build and installation instructions are given in the README file distributed together with the software. A step-by-step guide for Debian binary installation can be found in the appendix \ref{Debian install} Installation from Debian binary packages.
\section{ARCLIB gLite gateway plugin}
\label{ARCLIB gLite gateway plugin}
The ARCLIB gLite gateway plugin constist of the wrapper classes, the job description handling facility and the gLite specific CREAMClient base class. The wrapper classes coveys the function provided by the CREAMClient to ARCLIB. The job description handling framework makes a general job request representation available for the other classes. CREAMClient base class implements the interface towards CREAM2 computing elements.
This client object has an easy-to-use and intuitive interface. It uses the VOMS proxy certificate to build the secure channel to the server and to sign that of the server's.
The following sections present the set of functions provided by the library.\par
\subsection{Wrapper classes}
... mik ezek a wrapper osztályok ... milyen base class, mit csinál, mi a funckiójuk ... viszonylag részletesen ...
\subsection{Job description translators}
... Bárhol meghívható ... objektumot példányosítani ... milyen transzformációk állank rendelkezésre ...
\subsection{CREAMClient base class}
\label{CREAMClient}
The client object uses the VOMS proxy certificate to build the secure channel to the server and to sign that of the server's.\par
... 1 bekezdés arról, hogy SOAP a hed(Hivatkozni!!!) SOAP framework-jét használja 'fully integrated'... az előző deliverable-ben a kommunikáció gsoap-ot használt, ez az egyik nagy előrelépés, hogy ezt lecseréltük...
\subsubsection*{CREAMClient(Arc::URL, Arc::MCCConfig)}
\subsubsection*{setDelegationId(std::string)}
\subsubsection*{createDelegation(std::string)}
As almost every funtion, this one has no return value either. If there are any problems during the communication, either locally in the channel or at the remote site, the function throws \textit{CREAMClientError} described previously. If there are no exceptions thrown, then the command is considered to have successfully completed.
\subsubsection*{destroyDelegation(std::string)}
This method has the reverse functionality of the \textbf{createDelegation} function. It sends the \textit{destroy} message of CREAM2 to the remote server.
\subsubsection*{submit(std::string)}
\subsubsection*{stat(std::string)}
\subsubsection*{cancel(std::string)}
\subsubsection*{purge(std::string)}
\section{ARC command line tools for gLite CE}

@@

The well known ARC commands (ngsub, ngget, ... See: The Nordugrid/ARC User Guide\cite{userguide}!) will provide seemless access and integration with gLite computing elements. Full transparency will be achieved through the gLite gateway ARCLIB plugin. An ordinary user will use the same set of commands regardless of what type of CE to access. The user will be able to specify grid jobs described both in the gLite (JDL) and the Nordugrid (JSDL, XRSL) job description languages. ... +++Kipofozni. Hivatkozások... The client will perform automatic conversion between the different job description languages.\par
Unfortunately the interoperability features offered by the gLite gateway library are not yet integrated into the Nordugrid commands. Also the current version of ARCLIB does not offer the full spectrum of language transformations.
However only a set of temporary command line tools exposing the available features of library are provided. These temporary commands make the already existing interoparabilily features usable for ordinary users.

@@

\subsection{glitedelegate}
\label{glitedelegate}
In order to use gLite resources user must have a VOMS proxy. This proxy can be generated by command \textit{voms-proxy-init}.\par

@@

Once a VOMS proxy has been generated everything is in place to submit a new job. If one wants submit a job to a gLite server, first has to own a valid delegation on the remote site. This can either be an old, but still valid delegation identifier, or can be a new one. There is a command line tool to register a delegation on the CE to be used.\par
The usage of command \textbf{glitedelegate} is straighforward. All needed is a working CREAM2 delegation service URL, and a locally unique arbitrary delegation ID. This delegation ID will be associated to the remote resource. If you are not sure wether your favourite delegation ID is occupied or not, then try to delete it before registering it again. (See Section \ref{gliteundelegate} for further details!) The delegation command has the following syntax:
\begin{shaded}\verb#$ glitedelegate <delegation ID> <delegation service URL>#\end{shaded}
\begin{shaded}\verb#$ glitedelegate test_delegation \#\\*
\subsection{glitesub}
\label{glitesub}
The current command only supports direct job submission that is the user must know service endpoints. These kind of endpoints usually stored in LDAP databases. Ordinary ldapsearch can be used to find such an endpoint. Below an example:\par
... ldap parancs jön ide ...\par
The \textbf{glitesub} command implements the actual job submission in three phases: registration of a job, uploading the local files to the input sandbox URL received during the registration and starting the job.\par
The \textbf{glitesub} command requires a valid delegation. See Section \ref{glitedelegate} how to create one. By the way this is the only command which needs the delegation ID.\par The next step is to prepare the necessary input files and the job description!\par
The glitesub command syntax is the following (please note that the service URL, job description, info file are mandatory and can only be given in the specified order):
\begin{shaded}\verb#$ glitesub -D <delegation ID> <service URL> <job description> <info file>#\end{shaded}
Here the delegation ID is the identification registered previously. The service URL will be different than in the delegation example above, because this is not the URL of the delegation, but the execution service. The job description must be in JDL format like in the example below. The info file stores information about the job submitted. It should either be a non-existing file otherwise it is overwritten. This file contains the job ID, the input sandbox URL, the output sandbox URL and the service URL.\par
Below I present a JDL description example. Note that the \textit{VirtualOrganisation} and \textit{QueueName} attributes should be the same as your virtual organisation name and the corresponding queue name on the server side.\par

\begin{minipage}{\textwidth}
\begin{framed}
\verb#[#\\
\verb#Executable = "/bin/hostname";#\\
\verb#StdInput = "std.in";#\\
\verb#StdOutput = "std.out";#\\
\verb#StdError = "std.err";#\\
\verb#BatchSystem = "pbs";#\\
\verb#VirtualOrganisation = "knowarc.eu";#\\
\verb#InputSandbox = {"std.in"};#\\
\verb#OutputSandbox = {"std.out","std.err"};#\\
\verb#QueueName = "knowarc.eu";#\\
\verb#OutputSandboxDestURI = { "gsiftp://localhost/std.out", "gsiftp://localhost/std.err" };#\\
\verb#]#
\end{framed}
\end{minipage}

@@

... mit csinál a parancs sikeres és sikertelen futás esetén... \par

@@

The \textbf{glitestat} command contacts to the CREAM2 service on the service URL and queries job status of a job specified by the job ID given in the info file.\par

@@

The glitesub command implements a job status mapping between gLite and ARC job status semantics. The possible responses and their meanings are the following:

@@

\item ACCEPTING - the job submission is completed but the job is not yet scheduled
\item SUBMITTING - scheduling in progress
\item INLRMS:Q - the job is already at the local resource manager system and it is queued
\item INLRMS:R - the job is waiting at the local resource manager system for running
\item INLRMS:S - the job is running
\item KILLED - the job was terminated
\item FINISHED - the job has finished
\item FAILED - the job had some failure
\item FAILES - the job had some failure at LRMS level
\item EXECUTED - the job has been finished and there is no state information available

@@

The \textbf{glitekill} command can be used for killing a remote job running in the underlying batch system. The only necessary argument needed is the information file made by \textbf{glitesub}. (See Section \ref{glitesub} for further details!) This command initiates stopping the job in the batch system. You can check the effect by using \textbf{glitestat}. (See Section \ref{glitestat} for its usage!)\par

@@

Either after killing a job or because of some remote error occurs garbage files may remain on the server. These files can be purged by using command \textbf{gliteclean}. If you intentionally kill a job on the computing node, the job related stuff might also remain as garbage in the remote queue. This command also removes the job from the underlying batch system on the gLite computing element. It is important to note that this command removes the local information file as well. It might be useful to run this command after killing a job. (See Section \ref{glitekill}!)\par

@@

After the work is complete it is possible to unregister and delete the delegation entry from the remote site by using command \textbf{gliteundelegate}. It can also be used when one needs to register a delegation ID but are unsure whether it is already used or not. Put the delegation delegation service URL into the argument!\par

@@

\begin{shaded}\verb#$ gliteundelegate <delegation ID> <delegation service URL>#\end{shaded}

@@

\subsection{Skeleton of a temporary example gLite client}
Finally, here is an example code to present how easy and simple it is to write a new client using the CREAMClient class (See section \ref{CREAMClient}!). This code sample requests the job status of a previously submitted remote job, and writes it to the standard output. The client is written in C++.

@@

\section{Current limitations}
\label{Current limitations}

@@

\subsection{Unsupported CREAM features}

@@

\appendix
\section{Installation from Debian binary packages}
\label{Debian install}
This section contains instructions how to install the gateway libraries and glite* command line tools on Debian Linux.
\item Put the Debian repository into the APT source files (/etc/apt/sources.list). This repository in Luebeck is maintained as long as the KnowARC procject continues.
\item Update the package list and install the necessary dependencies:
\item Add the Globus libraries to the system path:
\item Install ARC1 client.
\item Create the vomses file:
\begin{shaded}\verb#$ mkdir -p /opt/glite/etc/#\end{shaded}
and copy these lines into the vomses file located at /opt/glite/etc/vomses
\bibliography{grid}
